\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-04-28 papers/paper1/ms.tex
adding OU process ref

@@

Similarly, setting both $b_j$ and $d_j$ to zero, we get
\begin{eqnarray}
k_j(\tau_{nm}) = a_j\,\exp\left(-c_j\,\tau_{nm}\right)
\end{eqnarray}
with the PSD
\begin{eqnarray}
S_j(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{a_j}{c_j}\,
    \frac{1}{1+{\left(\frac{\omega}{c_j}\right)}^2} \quad.
\end{eqnarray}
This model is often referred to as an Ornstein--Uhlenbeck process and this is
the kernel that was studied by Rybicki \& Press
\citep{Rybicki:1992,Rybicki:1995}.

>>>>

\newcommand{\response}[1]{{\color{green}#1}}

@@

Similarly, setting both $b_j$ and $d_j$ to zero, we get
\begin{eqnarray}
k_j(\tau_{nm}) = a_j\,\exp\left(-c_j\,\tau_{nm}\right)
\end{eqnarray}
with the PSD
\begin{eqnarray}
S_j(\omega) = \sqrt{\frac{2}{\pi}}\,\frac{a_j}{c_j}\,
    \frac{1}{1+{\left(\frac{\omega}{c_j}\right)}^2} \quad.
\end{eqnarray}
This model is often called an Ornstein--Uhlenbeck process \response{\citep[in
reference to the classic paper,][]{Uhlenbeck:1930}} and this is the kernel
that was studied by Rybicki \& Press \citep{Rybicki:1992,Rybicki:1995}.
